Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2023-02-26 Thesis/chapter/063-discussion.tex
free write phase 3

\subsection{Hindsight is easier than foresight}
%\subsection{Discussion}
%\todo{search i.e. and replace with i.e.\ }
%\todo{go to experimental and material (IV) discussion}
%\td{I-V: 2 terminal measurement one terminal was varibale and the other the ground from $-5*10^{-3}$ V to $5*10^{-3}$ V with steps of $10^{-2}$ measure current from back bone to backbone if shorted, then can measure actual resistance of layer. resistance of steel is neglectable. In order to get an impression of the quality of the layer mutliple contact (picture) are sputtered (throuhg a mask) and statistics: Two angabewerte: the weighted durchschnit and the number of pinholes, ie the number of contacts which were shorted, have an resistance below an threshold. if tunneling, iv follows powerlaw, if direct contact, iv follows linear }
%todo{go to anova discussion}
%- \td{The disadvantage of ANOVA is that information is lost because independent variables are assumed categorical even though they are ordinal}
%todo{british or US?} 
This subsection will discuss mistakes, improvements and lessons learned for each phase of this project in chronological order. 
Firstly, the 
\ref{sec:phase1} \textit{\nameref{sec:phase1}}, followed by the 
\ref{sec:phase2} \textit{\nameref{sec:phase2}}, thereupon the 
\ref{sec:phase3} \textit{\nameref{sec:phase3}} and finally the 
\ref{sec:phase3} \textit{\nameref{sec:phase4}}. 
%\subsubsection{Research, exploration and design phase}
%\subsubsection{Narrowing, pre-optimisation and constraint phase}
%\subsubsection{Optimisation, modelling and data generation}
%\subsubsection{Evaluation, interpretation and outlook phase}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Research, exploration and design phase}
\label{sec:phase1}
\td{freewriting}: \textbf{Scrutinize everthing!} At the beginning of a project it is importatnt 
to get a feel. I took the first recipe as only true recipe and tried to tune it to perfection. 
The problem was that the base line of that recipe was so low such that no matter how much I improved it, it was still bad. 
I only noticed this after trying out another recipe. 
My tipp here is to read as much and mostly diverse literature as possible and then try to mimic what ever you can. 
This will get you a "feel" of what works and what not. 
Thinking back to some design classes I took for data visualization: create as many and different designs as possible. 
Check what works, collect (dis-)advantages of methods and combine the best approaches. 
This can save you a lot of time.

@@

@@

>>>>

\subsection{Hindsight is easier than foresight}
%\subsection{Discussion}
%\todo{search i.e. and replace with i.e.\ }
%\todo{go to experimental and material (IV) discussion}
%\td{I-V: 2 terminal measurement one terminal was varibale and the other the ground from $-5*10^{-3}$ V to $5*10^{-3}$ V with steps of $10^{-2}$ measure current from back bone to backbone if shorted, then can measure actual resistance of layer. resistance of steel is neglectable. In order to get an impression of the quality of the layer mutliple contact (picture) are sputtered (throuhg a mask) and statistics: Two angabewerte: the weighted durchschnit and the number of pinholes, ie the number of contacts which were shorted, have an resistance below an threshold. if tunneling, iv follows powerlaw, if direct contact, iv follows linear }
%todo{go to anova discussion}
%- \td{The disadvantage of ANOVA is that information is lost because independent variables are assumed categorical even though they are ordinal}
%todo{british or US?: sation vs zation} 
This subsection will discuss mistakes, improvements and lessons learned for each phase of this project in chronological order. 
Firstly, the 
\ref{sec:phase1} \textit{\nameref{sec:phase1}}, followed by the 
\ref{sec:phase2} \textit{\nameref{sec:phase2}}, thereupon the 
\ref{sec:phase3} \textit{\nameref{sec:phase3}} and finally the 
\ref{sec:phase3} \textit{\nameref{sec:phase4}}. 
%\subsubsection{Research, exploration and design phase}
%\subsubsection{Narrowing, pre-optimisation and constraint phase}
%\subsubsection{Optimisation, modelling and data generation}
%\subsubsection{Evaluation, interpretation and outlook phase}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Research, exploration and design phase}
\label{sec:phase1}
\td{freewriting}: \textbf{Scrutinize everthing!} At the beginning of a project it is importatnt 
to get a feel. I took the first recipe as only true recipe and tried to tune it to perfection. 
The problem was that the base line of that recipe was so low such that no matter how much I improved it, it was still bad. 
I only noticed this after trying out another recipe. 
My tipp here is to read as much and mostly diverse literature as possible and then try to mimic what ever you can. 
This will get you a "feel" of what works and what not. 
Thinking back to some design classes I took for data visualization: create as many and different designs as possible. 
Check what works, collect (dis-)advantages of methods and combine the best approaches. 
This can save you a lot of time.

@@

\todo{include curse of dimensionality.}

@@

During the optimisation the main problems were too many in- and output variables, reproducability and regularisation. The first, problem was already discussed in the previous section. When working with stochastic algorithms it is especially important to be introduce reproducability via a seed, which determine all subsequent pseudo-random numbers. 
Finally, during the \gls{emma} optimisation es wurde auf regularisation verzichtet, 
because the regularization would be different 
because regularizing with the meand and std deviation would alter previous messurements, which alread beitragen to the model and the influence the decision of the next sample. 
On the other hand haette man auf jeden fall die input variablen normieren können. 
Normally, for standardisation the mean is substracted and it is devided by the standard deviation, which impplies a distribution of a random variable. 
One could have assumed a standard uniform distribution. 
rather $x'= \frac{x-\bar{x}}{x_{max} - \bar{x}}$ with $\bar{x}= x_{\text{max}} - x_{\text{min}}$
